DSSynth: An Automated Synthesis Tool of Digital Controllers \\ for Physical Plants via MATLAB Toolbox

### 2017-06-01 ase2017/paper.tex
added more comments related to the tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\title{DSSynth: An Automated Synthesis Tool for Physical Plants \\ Digital Controllers via MATLAB Toolbox}

@@

@@

@@

>>>>

\title{DSSynth: An Automated Synthesis Tool of Digital Controllers \\ for Physical Plants via MATLAB Toolbox}

@@

\textcolor{red}{Pascal, can you please review this paragraph?}

@@

\textcolor{red}{Lennon, can you please use an illustrative example related to UAV?}

@@

%---------------------------------------------------
\section{\tool Experimental Evaluation}
%---------------------------------------------------

%---------------------------------------------------
\subsection{Benchmarks Description}
%---------------------------------------------------

%---------------------------------------------------
\subsection{Objectives}
%---------------------------------------------------

%---------------------------------------------------
\subsection{Results}
%---------------------------------------------------
